SAT Competition 2020\tnoteref{title}

### 2020-09-29 paper/main.tex
more tables

\subsection{Main Track}

@@

\begin{table}[h]
\begin{tabular}{|l|l|l|}
\hline
Team & Solver & Configuration / Variant / Hack \\
\hline

@@

\multirow{2}{*}{\stack{Soos, Cai, }{Devriendt, Shaw}}
 & \multirow{2}{*}{CryptoMiniSat-CCAnr} & --\\
 &  & lsids\\
\hline

@@

\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}} & exp-V-LGB-MLD-CBT-DL & --\\
 & exp-V-L-MLDCBT-DL & --\\
 & exp-L-MLD-CBT-DL & -- \\
 & exp-V-MLD-CBT-DL & -- \\
\hline

\multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
 & \multirow{3}{*}{MapleCM} & +dist \\
 &  & +dist+sattime2s+- \\
 &  & +dist+simp2-- \\
 & MapleCMused & +dist \\
\hline

@@

Osama, Wijs & ParaFROST, ParaFROST-CBT & -- \\
\hline
\end{tabular}
\caption{Teams, Solvers and Hacks participating in the Main Tracks}
\end{table}

\subsection{Planning Track}

@@

@@

@@

>>>>

\subsection{Main Tracks}

This year in the Main Track, we had a Planning Sub-Track. 
The general idea is, that next to a balanced selection of benchmark instances in main track, to each year also offer one domain-specific sub-track.

@@

\begin{table}[h]
\begin{tabular}{|l|l|l|}
\hline
Team & Solver & Variant \\
\hline

@@

\multirow{2}{*}{\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}}~
 & \multirow{2}{*}{CryptoMiniSat-CCAnr} & --\\
 &  & lsids\\
\hline

@@

\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}}
 & \multirow{4}{*}{MapleLCMDistChronoBT-DL-v2.2} & exp-V-LGB-MLD-CBT-DL \\
 &  & exp-V-L-MLDCBT-DL \\
 &  & exp-L-MLD-CBT-DL \\
 &  & exp-V-MLD-CBT-DL \\
\hline

\multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
 & \multirow{4}{*}{MapleCM} & \texttt{+}dist \\
 &  & \texttt{+}dist\texttt{+}sattime2s\texttt{+}\texttt{-} \\
 &  & \texttt{+}dist\texttt{+}simp2\texttt{-}\texttt{-} \\
 &  & used\texttt{+}dist \\
\hline

@@

Osama, Wijs & ParaFROST, ParaFROST-CBT & -- \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the Main Tracks (Variant refers to a named configuration or a name of a hack)}
\end{table}

@@

\begin{table}[h]
\begin{tabular}{|l|l|}
\hline
Chen & abcdsat-i20 \\
\hline
\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & Cadical-sc2020 \\
\hline
\stack{Soos, Cai, }{Devriendt, Gocht, }{Shaw, Meel}~ & Cryptominisat-5 \\
\hline
Manthey & Riss-7.1.2\\
\hline
\end{tabular}
\caption{}
\end{table}

@@

\begin{table}[h]
\begin{tabular}{|l|l|}
\hline
\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
 & P-MCOMSPS-STR-32\\
 & P-MCOMSPS-STR-64\\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}
 & Plingeling\\
 & Treengeling\\
\hline
\multirow{2}{*}{Nabeshima, Inoue}
 & ManyGlucose-32\\
 & ManyGlucose-64\\
\hline
\multirow{2}{*}{Tchinda, Djamegni}
 & painlessmaplevone\\
 & painlessmaplevtwo\\
\hline
Li, Wu, Xu, Chen & syrupscavel\\
\hline
Chen & abcdsatptwenty\\
\hline
\end{tabular}
\caption{}
\end{table}

@@

\begin{table}[h]
\begin{tabular}{|l|l|}
\hline
Schreiber & mallob-mono\\
\hline
\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & TopoSAT2\\
\hline
Riveros & Slime\\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & Paracooba\\
& Paracooba-March\\
\hline
Hartung & CTSat\\
\hline
\end{tabular}
\end{table}
